---
title: "HW 02 - Water and Sanitation - Answer Key"
author: "Louis Quigley"
date: "`r Sys.Date()`"
output: github_document
---

## Load packages and data

```{r load-packages-data, message = FALSE}
library(tidyverse)
wat_san <- read_csv("data/water-and-sanitation.csv")
```

## Exercises

### Exercise 1

The dataset has `r nrow(wat_san)` rows.

### Exercise 2

The rows represent countries.

### Exercise 3

#The data says that over time, the percentage of people with no access to sanitation has decreased. The number of countries where everybody has access to sanitation has increased. 

```{r no-sanitation-years, fig.height=6, fig.width=6}
ggplot(wat_san, aes(sanitation_none)) +
  geom_histogram(binwidth = 9)+
  labs(
    x = "Percentage Pop",
    y = "Countries")+
  facet_wrap(~ Year, ncol = 5)
```

### Exercise 4

```{r bottom-5-2000}
wat_san %>% 
   filter(Year == 2000) %>% 
   arrange(desc(sanitation_none))
```
There doesn't seem to be a correlation between water none and sanitation none

### Exercise 5

The graph shows no correlation between sanitation and water access. 

```{r all-2000-plot}
wat_san %>% 
   filter(Year == 2000) %>% 
   ggplot(aes(water_none, sanitation_none)) +
     geom_point(alpha = .3)
```

### Exercise 6

Insert your answer here...

```{r bottom-5-2020}

```

### Exercise 7

Insert your answer here...

```{r progress-summary}
  
```

### Exercise 8

Insert your answer here...

```{r country-global-changes}

```
