---
title: "HW 02 - Water and Sanitation - Answer Key"
author: "Louis Quigley"
date: "`r Sys.Date()`"
output: github_document
---

## Load packages and data

```{r load-packages-data, message = FALSE}
library(tidyverse)
wat_san <- read_csv("data/water-and-sanitation.csv")
```

## Exercises

### Exercise 1

The dataset has `r nrow(wat_san)` rows.

### Exercise 2

The rows represent countries.

### Exercise 3

#The data says that over time, the percentage of people with no access to sanitation has decreased. The number of countries where everybody has access to sanitation has increased. 

```{r no-sanitation-years, fig.height=6, fig.width=6}
ggplot(wat_san, aes(sanitation_none)) +
  geom_histogram(binwidth = 9)+
  labs(
    x = "Percentage Pop",
    y = "Countries")+
  facet_wrap(~ Year, ncol = 5)
```

### Exercise 4

```{r bottom-5-2000}
wat_san %>% 
   filter(Year == 2000) %>% 
   arrange(desc(sanitation_none))
```
There doesn't seem to be a correlation between water none and sanitation none

### Exercise 5

The graph shows no correlation between sanitation and water access. 

```{r all-2000-plot}
wat_san %>% 
   filter(Year == 2000) %>% 
   ggplot(aes(water_none, sanitation_none)) +
     geom_point(alpha = .3)
```

### Exercise 6

The countries with high rates of no sanitation have changed between 2000 and 2020, but many of the same countries with no sanitation access remain at a high rate of no sanitation access. :(

```{r bottom-5-2020}
wat_san %>% 
   filter(Year == 2020) %>% 
   arrange(desc(sanitation_none))
```

### Exercise 7

The rates of no sanitation and no water has on average decreased across all countries between the years 2000 and 2020. This likely correlates with increased water and sanitation infrastructure in place around the world. 

```{r progress-summary}
wat_san %>% 
  filter(Year == 2000 & Entity != "World" | Year == 2020 & Entity != "World") %>% 
  # this line uses a combination of logical operators (== (equal to), & (and), != (is not equal to), | (or))
  # this combination filters for the two years provided, while excluding any data associated with the "World" Entity
  group_by(Year) %>% 
  # this line groups all the data by Year, so that any summary statistics specified below are computed for each group
  summarize(water_none_min = min(water_none, na.rm = T),
            water_none_mean = mean(water_none, na.rm = T),
            water_none_median = median(water_none, na.rm = T),
            water_none_stdev = sd(water_none, na.rm = T),
            water_none_iqr = IQR(water_none, na.rm = T),
            water_none_max = max(water_none, na.rm = T),
            
            sanitation_none_min = min(sanitation_none, na.rm = T),
            sanitation_none_mean = mean(sanitation_none, na.rm = T),
            sanitation_none_median = median(sanitation_none, na.rm = T),
            sanitation_none_stdev = sd(sanitation_none, na.rm = T),
            sanitation_none_iqr = IQR(sanitation_none, na.rm = T),
            sanitation_none_max = max(sanitation_none, na.rm = T)

            )
```

### Exercise 8

Insert your answer here...

```{r country-global-changes}

```
