---
title: "Lab 02 - Plastic waste"
author: "Louis Quigley"
date: "2/2/23"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

This is the plastic waste per capita by continent code and histograms.

```{r plastic-waste-continent}
ggplot(plastic_waste, aes(plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) +
facet_wrap(~ continent)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap, color = continent, fill = continent)) +
  geom_density(alpha = .11)
```

### Exercise 3

The color and fill I want to correlate with data, but the alpha I want to apply to the whole graph, so I put fill and color into the aes argument and alpha() into the geom_xxxx() argument. 

### Exercise 4

The violin plot shows the number of data points per plastic waste per capita as width of each figure. 

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()
```

### Exercise 5

The scatterplot reveals a slight positive correlation between increased plastic waste per capita and mismanaged plastic waste per capita. This means the more a country mismanages their plastic waste, the more likely they are to also produce more plastic waste. 

```{r plastic-waste-mismanaged}
ggplot(plastic_waste, aes(plastic_waste_per_cap, mismanaged_plastic_waste_per_cap)) +
  geom_point()
```

### Exercise 6

Europe has some of the highest rates of plastic waste per capita, but typically manages their waste better than other continents. North America also has high plastic waste per capita, but typically mismanage their plastic waste the most of other continents. :(

```{r plastic-waste-mismanaged-continent}
ggplot(plastic_waste, aes(plastic_waste_per_cap, mismanaged_plastic_waste_per_cap, color = continent)) +
  geom_point(alpha = .4)
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
