---
title: "Lab 02 - Plastic waste"
author: "Louis Quigley"
date: "2/2/23"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

This is the plastic waste per capita by continent code and histograms.

```{r plastic-waste-continent}
ggplot(plastic_waste, aes(plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) +
facet_wrap(~ continent)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap, color = continent, fill = continent)) +
  geom_density(alpha = .11)
```

### Exercise 3

The color and fill I want to correlate with data, but the alpha I want to apply to the whole graph, so I put fill and color into the aes argument and alpha() into the geom_xxxx() argument. 

### Exercise 4

The violin plot shows the number of data points per plastic waste per capita as width of each figure. 

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()
```

### Exercise 5

The scatterplot reveals a slight positive correlation between increased plastic waste per capita and mismanaged plastic waste per capita. This means the more a country mismanages their plastic waste, the more likely they are to also produce more plastic waste. 

```{r plastic-waste-mismanaged}
ggplot(plastic_waste, aes(plastic_waste_per_cap, mismanaged_plastic_waste_per_cap)) +
  geom_point()
```

### Exercise 6

Europe has some of the highest rates of plastic waste per capita, but typically manages their waste better than other continents. North America also has high plastic waste per capita, but typically mismanage their plastic waste the most of other continents. :(

```{r plastic-waste-mismanaged-continent}
ggplot(plastic_waste, aes(plastic_waste_per_cap, mismanaged_plastic_waste_per_cap, color = continent)) +
  geom_point(alpha = .4)
```

### Exercise 7

I plotted population data on the x-axis and plastic waste per capita on the y-axis, because it makes clearer that increases in coastal population does not significantly increase plastic waste per cap. 

```{r plastic-waste-population-total}
ggplot(plastic_waste, aes(total_pop, plastic_waste_per_cap, color = continent)) +
  geom_point(alpha = .25)
```

```{r plastic-waste-population-coastal}
ggplot(plastic_waste, aes(coastal_pop, plastic_waste_per_cap, color = continent)) +
  geom_point(alpha = .25)
```

### Exercise 8

This graph gets the proportion of the population which lives on the coast by dividing the data sets coastal_pop/total_pop. It then plots the proportion of the population living on the coast with the plastic waste per capita. It then filters out the Trinidad by only using data from plastic_waste_per_capita of values below 3. Each plot point is color coded by continent. Geom_smooth() shows a trend line of the data. 

```{r recreate-viz}
plastic_waste %>% 
  mutate(coastal_pop_prop = coastal_pop / total_pop) %>%
  filter(plastic_waste_per_cap < 3) %>%
  ggplot(aes(x = coastal_pop_prop, y = plastic_waste_per_cap, color = continent)) + 
    geom_point() +
    geom_smooth(color = "black") +
    scale_color_viridis_d() +
    labs(x = "Coastal population proportion (Coastal / total population)", 
         y = "Plastic waste per capita ", 
         color = "Continent",
         title = "Plastic waste vs. coastal population proportion",
         subtitle = "by continent") +
    theme_minimal()
```
