---
title: "Lab 02 - Plastic waste"
author: "Louis Quigley"
date: "2/2/23"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

This is the plastic waste per capita by continent code and histograms.

```{r plastic-waste-continent}
ggplot(plastic_waste, aes(plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) +
facet_wrap(~ continent)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap, color = continent, fill = continent)) +
  geom_density(alpha = .11)
```

### Exercise 3

The color and fill I want to correlate with data, but the alpha I want to apply to the whole graph, so I put fill and color into the aes argument and alpha() into the geom_xxxx() argument. 

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
